Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2023-11-20 lqg-strings.tex
Reorganized the main file sections and swapped x for y in the integration variable in first term of eq (25)

\subsection{The Bimetric String}\label{sec:bimetric-nambu-goto}

@@

Consider a string propagating in a target space whose geometry is described by two bulk metrics. There are two ways that a string with two metrics might arise. One possibility is that there are two sets of embedding fields $X^\mu$ and $Y^\mu$. As a result the induced metrics on the string worldsheet would also be different for both sets of embedding fields. However, in this case we would not be talking about \emph{one} string but two \emph{different} strings described by the respective embedding functions. One could then proceed along the lines of \eqref{eqn:hassan-bimetric} and introduce a third term for the worldsheet action which describes a coupling between the two sets of embedding fields, of the form:
\begin{equation}\label{eqn:ws-bimetric-interaction}
	S_{int} = - T_{eff} \int \diff^2 x\, \Phi(g,h) \Psi(\mb{X}, \mb{Y}).
\end{equation}
Here $\Phi(g,h)$ is some function of the \emph{induced} metrics $g_{ab}$ and $h_{ab}$ on the two worldsheets and $\Psi(\mb{X}, \mb{Y})$ is some function of the embedding fields. The resulting action would be of the form:
\begin{equation}\label{eqn:ws-bimetric-action-v1}
	S_{BNG} = -T \int \diff^2 x\, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
\end{equation}
Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''.

>>>>

\section{The Bimetric String}\label{sec:bimetric-nambu-goto}

@@

Consider a string propagating in a target space whose geometry is described by two bulk metrics. There are two ways that a string with two metrics might arise. One possibility is that there are two sets of embedding fields $X^\mu$ and $Y^\mu$. As a result the induced metrics on the string worldsheet would also be different for both sets of embedding fields. However, in this case we would not be talking about \emph{one} string but two \emph{different} strings described by the respective embedding functions. One could then proceed along the lines of \eqref{eqn:hassan-bimetric} and introduce a third term for the worldsheet action which describes a coupling between the two sets of embedding fields, of the form:
\begin{equation}\label{eqn:ws-bimetric-interaction}
	S_{int} = - T_{eff} \int \diff^2 x\, \Phi(g,h) \Psi(\mb{X}, \mb{Y}).
\end{equation}
Here $\Phi(g,h)$ is some function of the \emph{induced} metrics $g_{ab}$ and $h_{ab}$ on the two worldsheets and $\Psi(\mb{X}, \mb{Y})$ is some function of the embedding fields. The resulting action would be of the form:
\begin{equation}\label{eqn:ws-bimetric-action-v1}
	S_{BNG} = -T \int \diff^2 y \, \sqrt{-h} - T' \int \diff^2 x \, \sqrt{-g} + S_{int}.
\end{equation}
Here the subscript $BNG$ stands for ``Bimetric Nambu-Goto''.
